### 2016-01-18 paper.tex
Add two paragraphs from @nearyvs; fixes #43 and fixes #48

>>>>

The Reference Model Project (RMP), sponsored by the US Department of Energy,
launched six marine hydrokinetic (MHK) technology point designs as reference
models (RM) to serve as non-proprietary test articles for open research
development, and to benchmark performance and costs for technology developers
\cite{Neary2014, Neary2014a}. Open-source RMP products, along with supporting
documentation, are available at the RMP website
\url{http://energy.sandia.gov/rmp} to facilitate their use in future R\&D
studies by industry, academia, and national laboratories. These products
include: Design specifications and computer-aided design (CAD) files for each RM
device to allow exact replication for physical and numerical modeling studies;
Resource site information used to design each RM device; and references to
physical modeling data sets that can be used to validate numerical modeling
design and analysis tools.

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
that was designed to operate in a reach of the lower Mississippi River near
Baton Rouge, Louisiana \cite{Barone2011, Neary2011}.
